Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2025-12-16 Edith Zemanick/Sweat Variability/sweat_test_analysis.qmd
updated Cl filter, etc.

@@

```{r}
#| warning: false
group_n$pos = 4
ratiop_d <- ggplot(df, aes(x = Diagnosis, y = `Na:Cl`)) +
  geom_boxplot() +
  geom_label(
    data = group_n,
    aes(x = Diagnosis, y = pos, label = paste("n =", n))
  ) +
  geom_hline(yintercept = 1, color = "red") +
  geom_hline(yintercept = 1.25, color = "red") +
  theme_bw() +
  ylab("Na:Cl")
ratiop_d
```

@@

```{r}
#| warning: false
geno_n$pos = 4
ratiop_g <- ggplot(df, aes(x = `Genotype Risk`, y = `Na:Cl`)) +
  geom_boxplot() +
  geom_label(
    data = geno_n,
    aes(x = `Genotype Risk`, y = pos, label = paste("n =", n))
  ) +
  geom_hline(yintercept = 1, color = "red") +
  geom_hline(yintercept = 1.25, color = "red") +
  theme_bw() +
  ylab("Na:Cl")
ratiop_g
```

@@

```{r}
# Fit a multiclass ROC
mc_roc <- multiclass.roc(df$Diagnosis, df$`Na:Cl`, quiet = T)
roc_list <- list(
  "Cystic Fibrosis vs. Non-CF" = mc_roc$rocs[[2]],
  "CFTR-RD or CRMS vs. Cystic Fibrosis" = mc_roc$rocs[[1]],
  "CFTR-RD or CRMS vs. Non-CF" = mc_roc$rocs[[3]]
)
ggroc(roc_list, legacy.axes = T) +
  theme_bw() +
  theme(legend.title = element_blank())
roc_table <- lapply(roc_list, function(r) {
  coords(
    r,
    "best",
    best.method = "youden",
    ret = c(
      "threshold",
      "sensitivity",
      "specificity",
      "accuracy",
      "tpr",
      "fpr",
      "tnr",
      "fnr"
    )
  )
})
roc_table <- do.call(rbind, roc_table)
kable(roc_table, digits = 3)
```

@@

# Excluding Cl $\leq$ 30

```{r}
df <- df %>% filter(Cl > 30)
```

>>>>

setwd(home_dir)

@@

```{r}
#| warning: false
group_n$pos = 4
ratiop_d <- ggplot(df, aes(x = Diagnosis, y = `Na:Cl`)) +
  geom_boxplot() +
  geom_label(
    data = group_n,
    aes(x = Diagnosis, y = pos, label = paste("n =", n))
  ) +
  theme_bw() +
  ylab("Na:Cl")
ratiop_d
```

@@

```{r}
#| warning: false
geno_n$pos = 4
ratiop_g <- ggplot(df, aes(x = `Genotype Risk`, y = `Na:Cl`)) +
  geom_boxplot() +
  geom_label(
    data = geno_n,
    aes(x = `Genotype Risk`, y = pos, label = paste("n =", n))
  ) +
  theme_bw() +
  ylab("Na:Cl")
ratiop_g
```

@@

```{r}
# Fit a multiclass ROC
mc_roc <- multiclass.roc(
  df$Diagnosis,
  df$`Na:Cl`,
  quiet = T,
  levels = c("Non-CF", "CFTR-RD or CRMS", "Cystic Fibrosis")
)
roc_list <- list(
  "Cystic Fibrosis vs. Non-CF" = mc_roc$rocs[[2]],
  "CFTR-RD or CRMS vs. Cystic Fibrosis" = mc_roc$rocs[[3]],
  "CFTR-RD or CRMS vs. Non-CF" = mc_roc$rocs[[1]]
)
ggroc(roc_list, legacy.axes = T) +
  theme_bw() +
  theme(legend.title = element_blank())
roc_table <- lapply(roc_list, function(r) {
  coords(
    r,
    "best",
    best.method = "youden",
    ret = c(
      "threshold",
      "sensitivity",
      "specificity",
      "accuracy",
      "tpr",
      "fpr",
      "tnr",
      "fnr"
    )
  )
})
roc_table <- do.call(rbind, roc_table)
kable(roc_table, digits = 3)
```

@@

# Excluding Cl < 30

```{r}
df <- df %>% filter(Cl >= 30)
```
